### 2020-06-05 report/sections/server/react/alt.tex
Report: progress on chapter 5 limitations

\section{EFSM Encoding}
\label{section:reactefsm}

\begin{itemize}
\item motivated by the idea of model types, each state is encoded as a react component, where the user provides a view function (i.e. render())
\item channel actions are abstracted by the runtime and passed to state implementations as props
\item the developer provides an implementation of the state, i.e. ``uses the APIs'', by extending the abstract base classes and providing their own implementations
\end{itemize}

\subsection{Send}
\begin{itemize}
\item make the assumption that channel send actions are triggered by UI elements -- for example, clicking a button or typing enter in a textbox
\item pre-session-types -- the developer will attach an event listener
\item enhanced factory approach -- given an event and a event handler, return a react component that binds the handler to that event, and injects the channel action; the developer can use this API by putting the UI elements that represent the event action as children.
\item the event handler is conditionally parameterised by the event type (achievable by typescript conditional types -- eg, if event is click, then the event handler parameter is a React.MouseEvent), and the return type is the payload type
\item the abstract base class will set up the factory methods to be used by the developer
\end{itemize}

\subsubsection{Alternative Designs}
\begin{itemize}
\item not sure whether to put this in the subsection above so it flows better?
\item naive implementation is to pass the send() function as a prop for the developer to incorporate in their event listener -- this is most flexible, but we cannot provide static guarantees
\item factory approach -- the runtime could pass a factory function which, takes an UI element and performs the binding; this is better, as channel resources are not exposed, but the adversarial-minded developer can later override the event listener in the DOM etc
\end{itemize}

\subsection{Receive}
\begin{itemize}
\item receive state is `shown' when waiting for a receive event
\item base class has abstract methods -- one for each possible receive -- so the user must implement these when they extend the abstract base class
\item each abstract method is named after the message label expected to be received, and parameterised by the payload
\item no channel actions are passed to the state -- instead, once the receive state is mounted on the DOM (i.e. rendered), the abstract base class will register the event handlers to the runtime (using the register method passed as props)
\item when the message arrives, the runtime will invoke the registered function (+ forward reference the next section with the edge case that the message arrives before handler registration occurs)
\end{itemize}

\subsection{Terminal}
\begin{itemize}
\item by convention and design choice, the client gracefully closes the connection with the server role
\end{itemize}

>>>>

\section{Alternative Designs}
\begin{itemize}
\item not sure whether to put this in the subsection above so it flows better?
\item naive implementation is to pass the send() function as a prop for the developer to incorporate in their event listener -- this is most flexible, but we cannot provide static guarantees
\item factory approach -- the runtime could pass a factory function which, takes an UI element and performs the binding; this is better, as channel resources are not exposed, but the adversarial-minded developer can later override the event listener in the DOM etc
\end{itemize}

### 2020-06-05 report/sections/server/react/efsm.tex
Report: progress on chapter 5 approach
Report: complete chapter 5 approach
Report: progress on chapter 5 limitations

\section{State Encodings}

@@

\subsubsection{Alternative Designs}
\begin{itemize}
\item not sure whether to put this in the subsection above so it flows better?
\item naive implementation is to pass the send() function as a prop for the developer to incorporate in their event listener -- this is most flexible, but we cannot provide static guarantees
\item factory approach -- the runtime could pass a factory function which, takes an UI element and performs the binding; this is better, as channel resources are not exposed, but the adversarial-minded developer can later override the event listener in the DOM etc
\end{itemize}

>>>>

\section{EFSM Encoding}
\label{section:reactefsm}

@@

### 2020-06-05 report/sections/server/react/limitations.tex
Report: progress on chapter 5 limitations

\section{Limitations}
\begin{itemize}
\item affine channel usage guarantees -- cannot statically guarantee that the factory is attached to an event visible on the DOM
\item decoupling communication state management from business logic state management -- runtime design does not permit passing non-communication-related data as props; need to use other methods for propagating applicaton data (such as React Context API or Redux)
\item the point above might not be a `limitation', but more of an encouragement to change practices because it makes sense, architecturally, to separate concerns
\end{itemize}

>>>>

\section{Limitations}
As discussed, our EFSM encoding provides \textbf{affine} channel
usage guarantees for send states as supposed to \textit{linear} usage
guarantees. Suppose we bind a send action to a
button click event -- strictly speaking,
even if we guarantee that the button can be clicked exactly once,
we cannot guarantee that the button will ever be clicked by the user.
However, existing work \cite{PureScript2019,MVU2020} 
share the same limitation, and we view this as an
inherent limitation in front-end development, since there is
a limit to the types of assumptions we can make about how the
user interacts with the browser.
Redefining the definition of channel linearity 
for GUI programming use cases
would be an interesting discussion.

Our runtime implementation also limits the developer from
passing data into their EFSM state component through props.
This is because the runtime takes full control of which
state component to render, and by definition, what props 
are passed to the EFSM state components.
However, we equally view this as a way to encourage developers
to decouple communication state management from
business logic state management, in the spirit
of separating concerns.
In \cref{chap:eval},
we present examples of developer implementations
that use separate abstractions (such as the React Context API or
the third-party Redux library) for propagating 
stateful application data in \cref{chap:eval}.
